---
output: html_document
---
# Reproducible Research: Peer Assessment 1
Lets first install the data.table package and load it. This package makes life easy for us later when summing up and creating time series plots
```{r}
library(data.table)
```
Now lets load up the data. We assume activity.zip is in our working directory.
## Loading and preprocessing the data
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
ACTIVITY <- data.table(activity)
setkey(ACTIVITY,date)
```
## What is mean total number of steps taken per day?
```{r}
stepsByDate <- ACTIVITY[,sum(steps,na.rm = TRUE),by=date];
hist(x=stepsByDate$V1,plot=TRUE);
sprintf("Mean steps = %.0f",mean(stepsByDate$V1));
sprintf("Median steps = %.0f",median(stepsByDate$V1));
```
## What is the average daily activity pattern?
```{r}
stepsByInterval <- ACTIVITY[,mean(steps,na.rm=TRUE),by=interval]
plot(x <- stepsByInterval$interval,y<- stepsByInterval$V1, type = "l",xlab = "Interval",ylab = "Steps")
maxSteps <- max(stepsByInterval$V1)
maxInterval <- stepsByInterval$interval[which.max(stepsByInterval$V1)]
abline(v=maxInterval,col=3)
axis(side=1,at=maxInterval,col=3)
sprintf("Interval %.0f has the maximum average number of steps of %.0f",maxInterval,maxSteps)
```
## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
